---
title: "KPMB Data Analytics Virtual Experience"
output: html_notebook
---

By: Nugroho Budianggoro
02/12/2021
Jakarta, Indonesia

Checking parts of data that need cleaning.


```{r}
# Import
library("readxl")
library("dplyr")
library("ggplot2")
library("lubridate")
library("janitor")
library("tibble")

# Set path
path <- "KPMG_VI_New_raw_data_update_final.xlsx"

# Get sheets name
excel_sheets(path = path)

```
Define common procedures
```{r}
stats_cat <- function(col){
    num_row <- nrow(col)
    num_na <- sum(is.na(col))
    num_dup <- sum(duplicated(col))
    num_unique <- nrow(unique(col))
    
    Variable <- c("Number of Rows", "Number of NAs", "Number of Duplicates", "Number of Uniques")
    Value <- c(num_row, num_na, num_dup, num_unique)
    res <- data.frame(Variable, Value)
    return(res)
}

stats_num <- function(col){
    num_row <- nrow(col)
    min <- min(col, na.rm = TRUE)
    max <- max(col, na.rm=TRUE)
    num_na <- sum(is.na(col))
    num_dup <- sum(duplicated(col))
    num_unique <- nrow(unique(col))
    
    Variable <- c("Number of Rows", "Min", "Max", "Number of NAs", "Number of Duplicates", "Number of Uniques")
    Value <- c(num_row, min, max, num_na, num_dup, num_unique)
    res <- data.frame(Variable, Value)
    return(res)
}

stats_date <- function(col){
    num_row <- nrow(col)
    num_na <- sum(is.na(col))
    num_dup <- sum(duplicated(col))
    num_unique <- nrow(unique(col))
    
    Variable <- c("Number of Rows", "Number of NAs", "Number of Duplicates", "Number of Uniques")
    Value <- c(num_row, num_na, num_dup, num_unique)
    res <- data.frame(Variable, Value)
    return(res)
}

```

TRANSACTIONS sheet

```{r}
df_trans <- read_excel(path, sheet = "Transactions", skip = 1)
head(df_trans)

```

```{r}
# Change columns data types
to_chr <- c("transaction_id", "product_id", "customer_id")
df_trans[to_chr] <- sapply(df_trans[to_chr], as.character)

df_trans["product_first_sold_date"] <- excel_numeric_to_date(df_trans$product_first_sold_date)

```
TRANSACTIONS sheet: transaction_id

```{r}
stats_cat(df_trans["transaction_id"])
```
TRANSACTIONS sheet: product_id
```{r}
stats_cat(df_trans["product_id"])
```
```{r}
# Unique values
uniques <- unique(df_trans["product_id"])
pull(uniques, product_id)
```
TRANSACTIONS sheet: customer_id
```{r}
stats_cat(df_trans["customer_id"])
```
TRANSACTIONS sheet: transaction_date
```{r}
stats_date(df_trans["transaction_date"])

```
```{r}
min <- min(df_trans$transaction_date, na.rm = TRUE)
max <- max(df_trans$transaction_date, na.rm = TRUE)
data.frame(min, max)

```
```{r}
ggplot(df_trans, aes(x=transaction_date)) + geom_histogram()
```

TRANSACTIONS sheet: online_order
```{r}
stats_cat(df_trans["online_order"])
```
```{r}
unique(df_trans["online_order"])
```
```{r}
ggplot(df_trans["online_order"], aes(x=online_order)) + geom_bar()
```
TRANSACTIONS sheet: order_status
```{r}
stats_cat(df_trans["order_status"])
```

```{r}
ggplot(df_trans["order_status"], aes(x=order_status)) + geom_bar()
```
TRANSACTIONS sheet: brand
```{r}
stats_cat(df_trans["brand"])
```
```{r}
unique(df_trans["brand"])
```
```{r}
ggplot(df_trans["brand"], aes(x=brand)) + geom_bar()
```
TRANSACTIONS sheet: product_line
```{r}
stats_cat(df_trans["product_line"])
```
```{r}
unique(df_trans["product_line"])
```
```{r}
ggplot(df_trans["product_line"], aes(x=product_line)) + geom_bar()
```
TRANSACTIONS sheet: product_size

```{r}
stats_cat(df_trans["product_size"])
```
```{r}
unique(df_trans["product_size"])
```
```{r}

ggplot(df_trans["product_size"], aes(x=product_size)) + geom_bar()
```
TRANSACTIONS sheet: list_price
```{r}
stats_num(df_trans["list_price"])
```
```{r}
ggplot(df_trans, aes(x=list_price)) + geom_histogram()

```

```{r}
# Check to see if there is a character value in this numeric column
vec <- pull(df_trans, list_price )
sum(is.na(as.numeric(as.character(vec))))
```
TRANSACTIONS sheet: standard_cost

```{r}
stats_num(df_trans["standard_cost"])
```
```{r}
ggplot(df_trans, aes(x=standard_cost)) + geom_histogram()

```
```{r}
# Check to see if there is a character value in this numeric column
vec <- pull(df_trans, standard_cost )
sum(is.na(as.numeric(as.character(vec))))
```

```{r}
# Check to see if there is a character value in this numeric column
vec <- pull(df_trans, standard_cost )
sum(is.na(as.numeric(as.character(vec))))
```

TRANSACTIONS sheet: product_first_sold_date
```{r}
stats_date(df_trans["product_first_sold_date"])
```


```{r}
min <- min(df_trans$product_first_sold_date, na.rm = TRUE)
max <- max(df_trans$product_first_sold_date, na.rm = TRUE)
data.frame(min, max)
```

NEWCUSTOMERLIST sheet

```{r}
df_nc <- read_excel(path, sheet = "NewCustomerList", skip = 1)
head(df_nc)

```

```{r}
names(df_nc)
```

```{r}
# Change columns data types
to_num <- c("past_3_years_bike_related_purchases", "property_valuation")
df_nc[to_num] <- sapply(df_nc[to_num], as.numeric)
df_nc <- mutate(df_nc, DOB = as.Date(DOB, format = "%Y-%m-%d"))
```

NEWCUSTOMERLIST sheet: check for person duplicates

```{r}
df_nc$check_dup <- paste(df_ncl$first_name, df_ncl$last_name, df_ncl$DOB)
head(df_nc)
```
```{r}
stats_cat(df_nc["check_dup"])
```

NEWCUSTOMERLIST sheet: first_name

```{r}
stats_cat(df_nc["first_name"])
```

NEWCUSTOMERLIST sheet: last_name
```{r}
stats_cat(df_nc["last_name"])
```


NEWCUSTOMERLIST sheet: gender
```{r}
stats_cat(df_nc["gender"])
```
```{r}
unique(df_nc["gender"])
```
```{r}
ggplot(df_nc, aes(x=gender)) + geom_bar()
```
```{r}

as.data.frame(table(df_nc["gender"]))
```

NEWCUSTOMERLIST sheet: past_3_years_bike_related_purchases
```{r}
stats_num(df_nc["past_3_years_bike_related_purchases"])
```
```{r}
# Check if there is a non-numeric value in a numeric column
vec <- pull(df_nc, past_3_years_bike_related_purchases)
sum((is.na(as.numeric(as.character(vec)))))
```
```{r}
ggplot(df_nc, aes(x=past_3_years_bike_related_purchases)) + geom_histogram()
```


NEWCUSTOMERLIST sheet: DOB
```{r}
stats_date(df_nc["DOB"])
```
```{r}
min <- min(df_nc$DOB, na.rm=TRUE)
max <- max(df_nc$DOB, na.rm = TRUE)
data.frame(min, max)

```
```{r}
ggplot(df_nc, aes(x=DOB)) + geom_histogram()
```

NEWCUSTOMERLIST sheet: job_title
```{r}
stats_cat(df_nc["job_title"])
```
```{r}
unique <- unique(df_nc["job_title"])
unique <- unique[order(unique["job_title"]),]
pull(unique, job_title)
```
```{r}
table <- as.data.frame(table(df_nc["job_title"]))
table <- table[order(-table["Freq"]),]
table
```

NEWCUSTOMERLIST sheet: job_industry_category
```{r}
stats_cat(df_nc["job_industry_category"])
```
```{r}
unique(df_nc["job_industry_category"])
```
```{r}
ggplot(df_nc, aes(x=job_industry_category)) + geom_bar()
```


NEWCUSTOMERLIST sheet:

```{r}
stats_cat(df_nc["wealth_segment"])

```
```{r}
ggplot(df_nc, aes(x=wealth_segment)) + geom_bar()
```


NEWCUSTOMERLIST sheet: deceased_indicator

```{r}
stats_cat(df_nc["deceased_indicator"])
```



NEWCUSTOMERLIST sheet: owns_car
```{r}
stats_cat(df_nc["owns_car"])
```
```{r}
ggplot(df_nc, aes(x=owns_car)) + geom_bar()
```


NEWCUSTOMERLIST sheet:
```{r}
stats_num(df_nc["tenure"])
```
```{r}
ggplot(df_nc, aes(x=tenure)) + geom_histogram()
```
```{r}
table <- as.data.frame(table(df_nc["tenure"]))
table <- table[order(table["Freq"]),]
table
```

NEWCUSTOMERLIST sheet: address
```{r}
stats_cat(df_nc["address"])
```


NEWCUSTOMERLIST sheet: post_code
```{r}
stats_cat(df_nc["postcode"])
```
```{r}
# Check if there is a non-numeric value in a numeric column
vec <- pull(df_nc, postcode)
sum((is.na(as.numeric(as.character(vec)))))
```


NEWCUSTOMERLIST sheet: state
```{r}
stats_cat(df_nc["state"])
```
```{r}
unique(df_nc["state"])
```
```{r}
ggplot(df_nc, aes(x=state)) + geom_bar()
```


NEWCUSTOMERLIST sheet: country
```{r}
stats_cat(df_nc["country"])
```


NEWCUSTOMERLIST sheet: property_valuation
```{r}
stats_num(df_nc["property_valuation"])
```
```{r}
# Check if there is a non-numeric value in a numeric column
vec <- pull(df_nc, property_valuation)
sum((is.na(as.numeric(as.character(vec)))))
```
```{r}
ggplot(df_nc, aes(x=property_valuation)) + geom_histogram()
```


NEWCUSTOMERLIST sheet: rank
```{r}
stats_num(df_nc["Rank"])
```
```{r}
table <- as.data.frame(table(df_nc["Rank"]))
table <- table[order(-table["Freq"]),]
table
```
```{r}
ggplot(df_nc, aes(x=Rank)) + geom_histogram()
```
```{r}
vec <- pull(df_nc, Rank)
sum((is.na(as.numeric(as.character(vec)))))
```


NEWCUSTOMERLIST sheet: Value
```{r}
stats_num(df_nc["Value"])
```
```{r}
vec <- pull(df_nc, Value)
sum((is.na(as.numeric(as.character(vec)))))
```
```{r}
ggplot(df_nc, aes(x=Value)) + geom_histogram()
```
CUSTOMERDEMOGRAPHIC sheet
```{r}
df_cd <- read_excel(path, sheet = "CustomerDemographic", skip = 1)
head(df_cd)
```
```{r}
# Change columns data types
to_num <- c("DOB")
df_cd[to_num] <- sapply(df_cd[to_num], as.numeric)
df_cd["DOB"] <- excel_numeric_to_date(df_cd$DOB)
# Customer with ID 4 has DOB 1843. It is visible in Excel but appeared to be turned to NA in R.

```
CUSTOMERDEMOGRAPHIC sheet: check for duplicates in customer names
```{r}
df_cd$check_dup <- paste(df_cd$first_name, df_cd$last_name, df_cd$DOB)
head(df_nc)
```
```{r}
stats_cat(df_cd["check_dup"])
```


CUSTOMERDEMOGRAPHIC sheet: customer_id
```{r}
# Check if there is a non-numeric value in a numeric column
vec <- pull(df_cd, customer_id)
sum((is.na(as.numeric(as.character(vec)))))
```
```{r}
stats_num(df_cd["customer_id"])
```


CUSTOMERDEMOGRAPHIC sheet: first_name
```{r}
stats_cat(df_cd["first_name"])
```


CUSTOMERDEMOGRAPHIC sheet: last_name
```{r}
stats_cat(df_cd["last_name"])
```


CUSTOMERDEMOGRAPHIC sheet: gender
```{r}
stats_cat(df_cd["gender"])
```
```{r}
unique(df_cd["gender"])
```
```{r}
as.data.frame(table(df_cd["gender"]))
```


CUSTOMERDEMOGRAPHIC sheet: past_3_years_bike_related_purchases
```{r}
stats_num(df_cd["past_3_years_bike_related_purchases"])
```
```{r}
ggplot(df_cd, aes(x=past_3_years_bike_related_purchases)) + geom_histogram()
```


CUSTOMERDEMOGRAPHIC sheet: DOB
```{r}
stats_date(df_cd["DOB"])
```
```{r}
min <- min(df_cd$DOB, na.rm = TRUE)
max <- max(df_cd$DOB, na.rm = TRUE)
data.frame(min, max)
```
```{r}
ggplot(df_cd, aes(x=DOB)) + geom_histogram()
```


CUSTOMERDEMOGRAPHIC sheet: job_title
```{r}
stats_cat(df_cd["job_title"])
```
```{r}
unique <- unique(df_cd["job_title"])
unique <- unique[order(unique["job_title"]),]
pull(unique, job_title)
```
```{r}
table <- as.data.frame(table(df_nc["job_title"]))
table <- table[order(-table["Freq"]),]
table
```


CUSTOMERDEMOGRAPHIC sheet: job_industry_category
```{r}
stats_cat(df_cd["job_industry_category"])
```
```{r}
unique <- unique(df_cd["job_industry_category"])
unique <- unique[order(unique["job_industry_category"]),]
pull(unique, job_industry_category)
```
```{r}
table <- as.data.frame(table(df_nc["job_industry_category"]))
table <- table[order(-table["Freq"]),]
table
```


CUSTOMERDEMOGRAPHIC sheet: wealth_segment
```{r}
stats_cat(df_cd["wealth_segment"])
```
```{r}
unique(df_cd["wealth_segment"])
```
```{r}
ggplot(df_cd, aes(x=wealth_segment)) + geom_bar()
```


CUSTOMERDEMOGRAPHIC sheet:
```{r}
stats_cat(df_cd["deceased_indicator"])
```
```{r}
as.data.frame(table(df_cd["deceased_indicator"]))
```



CUSTOMERDEMOGRAPHIC sheet: owns_car
```{r}
stats_cat(df_cd["owns_car"])
```
```{r}
as.data.frame(table(df_cd["owns_car"]))
```

CUSTOMERDEMOGRAPHIC sheet: tenure

```{r}
stats_num(df_cd["tenure"])
```
```{r}
ggplot(df_cd, aes(x=tenure)) + geom_histogram()
```
CUSTOMERADDRESS sheet
```{r}
df_ca <- read_excel(path, sheet = "CustomerAddress", skip = 1)
head(df_ca)

```
```{r}
# Change columns data types
df_ca["postcode"] <- sapply(df_ca['postcode'], as.numeric)
```

CUSTOMERADDRESS sheet: customer_id
```{r}
vec <- pull(df_ca, customer_id)
sum((is.na(as.numeric(as.character(vec)))))
```
```{r}
stats_num(df_ca["customer_id"])
```


CUSTOMERADDRESS sheet:
```{r}
stats_cat(df_ca["address"])
```


CUSTOMERADDRESS sheet:
```{r}
stats_num(df_ca["postcode"])
```


CUSTOMERADDRESS sheet: state
```{r}
stats_cat(df_ca["state"])
```
```{r}
unique(df_ca["state"])
```
```{r}
ggplot(df_ca, aes(x=state)) + geom_bar()
```


CUSTOMERADDRESS sheet: country
```{r}
stats_cat(df_ca["country"])
```


CUSTOMERADDRESS sheet: property_valuation
```{r}
stats_num(df_ca["property_valuation"])
```
```{r}
ggplot(df_ca["property_valuation"], aes(x=property_valuation)) + geom_histogram()
```

